Union and Intersection Contracts Are Hard, Actually

### 2021-09-16 paper.tex
Capitalize headings
Use pbalance for balancing, update copyright information

\documentclass[sigplan,screen,10pt]{acmart}
%\usepackage{amssymb}
\usepackage{mathtools,amsmath,amsfonts,amsxtra,amsthm,mathrsfs,mathpartir}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{array}
\usepackage[toc,page]{appendix}
\usepackage{graphicx}
\usepackage{varioref}
\usepackage{verbatim,comment}
\usepackage{longtable}
\usepackage{tikz}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{microtype}

@@

\title{Union and intersection contracts are hard, actually}
\author{Teodoro Freund}
\affiliation{
  \institution{Universidad de Buenos Aires}
  \city{Buenos Aires}
  \country{Argentina}
}
\email{tfreund@dc.uba.ar}

@@

%%% If you see 'ACMUNKNOWN' in the 'setcopyright' statement below,
%%% please first submit your publishing-rights agreement with ACM (follow link on submission page).
%%% Then please update our instructions page and copy-and-paste the NEW commands into your article.
%%% Please contact us in case of questions; allow up to 10 min for the system to propagate the information.
%%%
%%% The following is specific to DLS '21 and the paper
%%% 'Union and Intersection Contracts Are Hard, Actually'
%%% by Teodoro Freund, Yann Hamdaoui, and Arnaud Spiwack.
%%%
\setcopyright{ACMUNKNOWN}
\acmPrice{15.00}
\acmDOI{10.1145/3486602.3486767}
\acmYear{2021}
\copyrightyear{2021}
\acmSubmissionID{splashws21dlsmain-p31-p}
\acmISBN{978-1-4503-9105-4/21/10}
\acmConference[DLS '21]{Proceedings of the 17th ACM SIGPLAN International Symposium on Dynamic Languages}{October 19, 2021}{Chicago, IL, USA}
\acmBooktitle{Proceedings of the 17th ACM SIGPLAN International Symposium on Dynamic Languages (DLS '21), October 19, 2021, Chicago, IL, USA}

@@

\subsection{Configuration languages}

@@

\section{A typology of language features}
\label{sec:feat-lang}

@@

\subsection{Referential transparency}
\label{sec:optimizations}

@@

\section{Union \& intersection}
\label{sec:union-inter}

@@

\paragraph{In gradually typed systems}

@@

\subsection{Union contracts as a side-effect}

@@

\subsection{Intersection with user-defined contracts}
\label{sec:flat-and-inter}

@@

\section{Pragmatic trade-offs}
\label{sec:issues-literature}

@@

\subsection{A coinductive semantics}
\label{sec:coinductive-sem}

@@

\subsection{A first realization}
\label{sec:keil-thiemann}

@@

\subsection{Monitoring properties}
\label{sec:will-morr-wadl}

@@

\section{(More) Related work}
\label{sec:related-work}
\info{Including a mention of statically typed systems with union}

@@

\subsection{Higher-order contracts}

@@

\subsection{Unions and intersections in gradual typing}

@@

\subsection{Context sensitive contracts}

>>>>

\documentclass[sigplan,screen,10pt]{acmart}
%\usepackage{amssymb}
\usepackage{mathtools,amsmath,amsfonts,amsxtra,amsthm,mathrsfs,mathpartir}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{array}
\usepackage[toc,page]{appendix}
\usepackage{graphicx}
\usepackage{varioref}
\usepackage{verbatim,comment}
\usepackage{longtable}
\usepackage{tikz}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{pbalance}

@@

\title{Union and Intersection Contracts Are Hard, Actually}
\author{Teodoro Freund}
\affiliation{
  \institution{Universidad de Buenos Aires}
  \city{Buenos Aires}
  \country{Argentina}
}
\email{tfreund@dc.uba.ar}

@@

%%% The following is specific to DLS '21 and the paper
%%% 'Union and Intersection Contracts Are Hard, Actually'
%%% by Teodoro Freund, Yann Hamdaoui, and Arnaud Spiwack.
\copyrightyear{2021}
\acmYear{2021}
\setcopyright{acmlicensed}\acmConference[DLS '21]{Proceeding of the 17th ACM SIGPLAN International Symposium on Dynamic Languages}{October 19, 2021}{Chicago, IL, USA}
\acmBooktitle{Proceeding of the 17th ACM SIGPLAN International Symposium on Dynamic Languages (DLS '21), October 19, 2021, Chicago, IL, USA}
\acmPrice{15.00}
\acmDOI{10.1145/3486602.3486767}
\acmISBN{978-1-4503-9105-4/21/10}

\acmConference[DLS '21]{Proceedings of the 17th ACM SIGPLAN International Symposium on Dynamic Languages}{October 19, 2021}{Chicago, IL, USA}
\acmBooktitle{Proceedings of the 17th ACM SIGPLAN International Symposium on Dynamic Languages (DLS '21), October 19, 2021, Chicago, IL, USA}

@@

\subsection{Configuration Languages}

@@

\section{A Typology Of Language Features}
\label{sec:feat-lang}

@@

\subsection{Referential Transparency}
\label{sec:optimizations}

@@

\section{Union \& Intersection}
\label{sec:union-inter}

@@

\paragraph{In Gradually Typed Systems}

@@

\subsection{Union Contracts as a Side-Effect}

@@

\subsection{Intersection With User-Defined Contracts}
\label{sec:flat-and-inter}

@@

\section{Pragmatic Trade-Offs}
\label{sec:issues-literature}

@@

\subsection{A Coinductive Semantics}
\label{sec:coinductive-sem}

@@

\subsection{A First Realization}
\label{sec:keil-thiemann}

@@

\subsection{Monitoring Properties}
\label{sec:will-morr-wadl}

@@

\section{(More) Related Work}
\label{sec:related-work}
\info{Including a mention of statically typed systems with union}

@@

\subsection{Higher-Order Contracts}

@@

\subsection{Unions and Intersections in Gradual Typing}

@@

\subsection{Context Sensitive Contracts}
